Titeln på avhandlingens språk

### 2022-09-29 model.tex
updating to new models

\begin{table}
    \centering
    \caption[A]{%
        Sample of the execution time data  used for the elaboration of the timing model.
        Rows contain the execution times and \acp{TTF} for each of the \num{169} steps performed by the \num{40} participants in \textcite{olguinmunoz:impact2021}, expressed in seconds, together with a unique identifier for the subject, their associated level of normalized neuroticism, and a sequence number identifying the position of the step in the task.
    }\label{tab:data:exectime}
    \begin{tabular}{rrrrrr}
        \toprule
        {seq}        & {run\_id}    & {exec\_time} & {ttf}        & {neuroticism} \\
        \midrule
        1            & 134146       & 3.655        & 0.597        & 0.375         \\
        2            & 134146       & 4.439        & 0.554        & 0.375         \\
        3            & 134146       & 2.943        & 0.562        & 0.375         \\
        \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)  \\
        169          & 134146       & 3.532        & 4.571        & 0.375         \\
        1            & 134470       & 3.461        & 0.561        & 0.594         \\
        2            & 134470       & 6.678        & 0.572        & 0.594         \\
        \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)  \\
        \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)  \\
        169          & 137353       & 4.615        & 0.537        & 0.625         \\
        \bottomrule
    \end{tabular}
\end{table}

We employ a cleaned and re-parameterized copy of the aforementioned timing data.
The \num{6760} data points are arranged in a table, a sample of which can be seen in \cref{tab:data:exectime}, together with identifiers for the subjects, their neuroticism score, and a sequence number for each step.

@@

Finally, we assign a number to each sample corresponding to \emph{how long} the current combination of level of impairment and transition has been in effect, in number of steps.
This count resets whenever this combination changes.
This value is subsequently discretized into three levels; \emph{short}, \emph{medium}, and \emph{long duration} (again, refer to \cref{tab:defaultbins} for the exact values used).

The results of this processing on the samples from \cref{tab:data:exectime} can be seen in \cref{tab:data:exectime:processed}.
Three examples of the effect of this discretization and processing on the data are also presented in \cref{fig:timing}.
Specifically, we showcase how
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; and}}]
    \item higher neuroticism leads to higher mean execution times as impairment goes up (\cref{fig:timing:impneurvsetime})
    \item duration has both a speed-up and slow-down effect on execution times, depending on the level of impairment (\cref{fig:timing:durvsetime})
    \item transitions from higher to lower levels of impairment lead to higher mean execution times when compared to steps far away from a transition, or from a transition from lower to higher levels of impairment (\cref{fig:timing:imptransvsetime})
\end{enumerate*}.

@@

\begin{table*}
    \todo[inline]{Remove this table, or re-do it.}
    \caption{Sample of the processed execution time data table.}\label{tab:data:exectime:processed}
    \begin{tabular}{rrrrcrccrc}
        \toprule
        {seq}        & {run\_id}    & {next\_exec\_time} & {ttf}        & {impairment} & {neuroticism\_raw} & {neuroticism} & {transition} & {duration\_raw} & {duration}   \\
        \midrule
        1            & 134146       & 3.655              & 0.000        & low          & 0.375              & low           & NoTransition & 1               & short        \\
        2            & 134146       & 4.439              & 0.597        & low          & 0.375              & low           & NoTransition & 2               & short        \\
        3            & 134146       & 2.943              & 0.554        & low          & 0.375              & low           & NoTransition & 3               & short        \\
        \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \)  & \( \cdots \) & \( \cdots \)    & \( \cdots \) \\
        169          & 134146       & 3.532              & 3.689        & high         & 0.375              & low           & Lower2Higher & 2               & short        \\
        1            & 134470       & 3.461              & 0.000        & low          & 0.594              & high          & NoTransition & 1               & short        \\
        2            & 134470       & 6.678              & 0.561        & low          & 0.594              & high          & NoTransition & 2               & short        \\
        \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \)  & \( \cdots \) & \( \cdots \)    & \( \cdots \) \\
        \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \) & \( \cdots \) & \( \cdots \)       & \( \cdots \)  & \( \cdots \) & \( \cdots \)    & \( \cdots \) \\
        169          & 137353       & 4.615              & 0.579        & low          & 0.625              & high          & NoTransition & 2               & short        \\
        \bottomrule
    \end{tabular}
\end{table*}

@@

\subsection{Model verification}\label{ssec:model:verification}
\todo[inline]{Needs better name.}
\todo[inline]{Rework with new tweaked models.}

>>>>

We employ a cleaned and re-parameterized copy of the aforementioned timing data.
The \num{6760} data points are arranged in a table together with identifiers for the subjects, their neuroticism score, and a sequence number for each step.

@@

Finally, we assign a number to each sample corresponding to \emph{how long} the system has been under the current level of impairment, in number of steps.
% This count resets whenever this combination changes.
This value is subsequently discretized into three levels; \emph{short}, \emph{medium}, and \emph{long duration} (again, refer to \cref{tab:defaultbins} for the exact values used).

% The results of this processing on the samples from \cref{tab:data:exectime} can be seen in \cref{tab:data:exectime:processed}.
Three examples of the effect of this discretization and processing on the data are presented in \cref{fig:timing}.
Specifically, we showcase how
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; and}}]
    \item higher neuroticism leads to higher mean execution times as impairment goes up (\cref{fig:timing:impneurvsetime})
    \item duration has both a speed-up and slow-down effect on execution times, depending on the level of impairment (\cref{fig:timing:durvsetime})
    \item transitions from higher to lower levels of impairment lead to higher mean execution times when compared to steps far away from a transition, or from a transition from lower to higher levels of impairment (\cref{fig:timing:imptransvsetime})
\end{enumerate*}.

@@

@@

\subsection{Model verification}\label{ssec:model:verification}
\todo[inline]{Needs better name.}
\todo[inline]{Rework with new tweaked models.}
\todo[inline]{Needs to include first the synthetic setup, then "real" setup.}
